Exploring and Predicting House Price in Nanjing: Geographically Imbalanced Distribution Across Districts and the Crucial Role of Unit Price and Bedroom Count in Predictioin

### 2023-12-08 output/paper/paper.qmd
Complete draft

---
title: "House Price in Nanjing: Comparing Multiple Linear Regression and Random Forest"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "House price in Nanjing has grown rapidly and became a concern in recent years. This paper examines the relationship between house price in Nanjing, structural attributes of the property, and location using open data collected from Lianjia.com, and predict house price in Nanjing with different models. We find a geographically-imbalanced distribution of house price in Nanjing with large variance within and between each district. By comparing the MAE and RMSE, we find the random forest model gives a better prediction accuracy than the multiple linear regression model. Further work could include geocoding data to perform spatial autocorrelation analysis that consider the spatial effect in the data. "
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---

@@

House prices in China has grown rapidly since 2000, and cities such as Shanghai, Beijing, and Shenzhen are among the highest around the world today [@citeHouseincrease]. Nanjing, which is located in the heart of Yangtze River Delta in eastern China and approximately 300 km from Shanghai, is the capital city for Jiangsu Province, one of the most economically developed provinces in China [@citeNanjing]. The house price in Nanjing has been a concern due to increased population in recent years [@citeConcern].

In this paper, we investigate how structural attributes and location of house affect the total house price and explore the characteristics of residential housing. We are also interested in predicting house price in Nanjing using different models. We use` Python` to collect data from Lianjia.com and `R` to clean and analyze collected data. We construct a multiple linear regression model with total house price explained by 9 other variables representing structural characteristics and location, and a random forest regression model with same variables. We find that the house price in Nanjing is geographically-imbalanced and even the variance within each district is large, indicating possible income and wealth inequality. Comparing two models with Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), we find that the random forest model gives a better prediction accuracy on both test and train data, indicating possible non-linear relationships between variables. Further work could include geospatial data to find spatial correlations and consider a more comprehensive model including more attributes such as surronding environment.

The remainder of this paper is structured as follows: @sec-data discusses the data with @sec-data_description including information about data collection and data cleaning results, and @sec-data_visualization including graphs and tables representing relationships between variables and distributions of variables; @sec-model introduces the split of train/test data and two models: a multiple linear regression model and a random forest regression model, and specifies parameters; @sec-result shows the estimates of fitted models and compares two models; @sec-discussion includes discussions about model results and implications with @sec-weakness talking about the weaknesses and future improvement.

# Data

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2expand` [@citeLatex2expand] to add title to figures, `knitr` [@citeKnitr] and `modelsummary` [@citeModelsummary] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to build up a random forest model and compare the results with multiple linear regression model using different metrics. The color style of the figures was created referring to a R colors cheet-sheet [@citeRcolor].

## Data description

The dataset in this analysis was obtained from Lianjia.com using a web scrapping program in Python [@citePython]. Lianjia.com is the website of one of the largest estate brokerage firm in China and the source is open and accessible [@citeLianjia]. We collected 11 datasets with over 30,000 observations for 11 different districts in Nanjing, China. To account for temporal variations of housing market, we specifically collected sales property price listed on 22 November, 2023 instead of posted transactions and to consider the consistency, we only collected data for residential houses and discarded data for other types of properties. The datasets includes listed sales prices and structural attributes of the properties including the floor area, the unit price per $m^2$, number of rooms, etc.

The original datasets were merged into one large dataset by districts with missing value removed. After obtaining 5 detailed structural characteristics by splitting `Structrual attributes` variable in original dataset, we created two new variables: `Detailed_Floor` and `Facing_South`. The variable `Detailed_Floor` was obtained from the variable `Total floor`. If the property is in high floor, the detailed floor will be the total floor multiplies by 0.7; if the property is in medium floor, the detailed floor will be the total floor multiplies by 0.45; and if the property is in low floor, the detailed floor will be the total floor multiplies by 0.2. The varible `Facing_South` is a dummy variable with 1 representing the house is south-facing and 0 otherwise. Definitions and descriptions for the 10 variables are listed in @tbl-data. Most of them captured the structural attributes of the house and only variable `District` indicated an approximate location of the house.

@@

#### Workspace setup ####
library(tidyverse)
library(knitr)
library(here)
library(latex2exp)
library(randomForest)
library(corrplot)
library(Metrics)
library(modelsummary)

@@

var <- c("Total_Price", "Unit_Price", "District", "Area", "Furnished", "Bedroom", "Living_Room", "Total_Floors", "Detailed_Floor", "Facing_South")
type <- c("Continuous", "Continuous", "Character", "Continuous", "Character", "Discrete", "Discrete", "Discrete", "Discrete", "Dummy")
def <- c("Total house price in ten-thousand yuan", "Unit house price in yuan per square meter", "District where the house is located", "Floor area of the house in square meter ", "Decoration status of the house", "Number of bedrooms", "Number of living/dining rooms", "Total floors of the building", "Floor level of the house", "Whether the house is facing south")
kable(data.frame(var, type, def), col.names = c("Variable", "Type", "Definition"))
```

## Data visualiztion

@tbl-price shows a summary for average total house price in ten-thousand yuan, average unit price in yuan/$m^2$, and average floor area in $m^2$ for 11 districts in Nanjing. We find that the highest average house price was in Jianye district while the lowest average house price was in Gaochun district, which is also consistent with the average unit price. However, the average floor area shows a different pattern that Qinhuai district had the smallest average floor area while Jianye and Pukou districts had the largest average floor area. The difference was not very large within 30 $m^2$. This may relate to geographical information for each districts since the area and population differ from each district. Different from relatively centered average floor area for each districts, the average house price and unit price show a larger variance. This may relate to business activities and industrial development in each district.

@@

data |> group_by(District) |>
  summarise(avg_total = round(mean(Total_Price)), 
            avg_unit = round(mean(Unit_Price)),
            avg_area = round(mean(Area))) |>
  kable(col.names = c("District", "Average total price",
                      "Average unit price", "Average floor area"))
```

@fig-con, @fig-dis, @fig-char basically explore the statistical features of the 9 explanatory variables. @fig-con shows the distribution for variable `Area`, `Total_Price`, and `Unit_Price`, @fig-dis shows the distribution for variable `Bedroom`, `Living_Room`, `Total_Floors`, and `Detailed_Floor`, and @fig-char shows the proportion of house with 4 different decoration status `Furnished` and orientations `Facing_South` in each district. We find that the total house price, the unit price, and the area were all right-skewed, which means there were less extremely high values for these variables, and the mean values were larger than the median ones. We can also find that most of the values centered in a range. The area mostly centered between 0 to 200 $m^2$, the total price mostly centered between 0 to 1,000 ten-thousand yuan, and the unit price had a larger range between 0 to 50,000 yuan.

@@

From @fig-dis we find that most of listed houses had 2 or 3 bedrooms and 1 to 2 living/dining rooms. The number of rooms was relatively simple with a few houses having over 4 bedrooms and 3 living/dining rooms. However, for total floors of the building and detailed floor, they were various. We find for total floors, there are 3 bursts in approximately 5, 10, and 20, which corresponded to 3 common types of residential buildings in China. However, for detailed floor of listed house, we find that they mostly centered at lower level of the building. This may relate to the sunshine condition as the residential buildings were higher and more dense recently, a lower level house may have a bad sunshine and lighting condition.

@@

We find from @fig-char that the numbers of house each districts in our data were similar excluding Gaochun district. This related to the web scrapping program we used to obtained the data. However, it indicates that the total number of housel listed in Gaochun district was limited. For the orientation of the house, we find that relatively half of the house is south-facing and in Lishui and Gaochun district the proportions were even higher. It shows a tradition in China that people tend to choose house facing south, which according to Chinese traditional Feng Shui has positive effect on someone's luck [@citeFengshui]. For decoration status of the house, the data was not that informative since type `Other` occupies a large proportion, which means the information is missing for the house. However, from existing data we find that fully furnished houses on sale has a larger proportion than partly furnished or not furnished house. This may relate to the data we collected that there were a lot of second-hand house on sale instead of newly closed. It is noticeable that house in Jianyi district had a much larger proportion of fully furnished house. This may related to the house type that there are more fully furnished luxury apartments in Jianyi since the Central Business District (CBD) is located there.

@@

@fig-area and @fig-price shows the how the total house price in each districts and Nanjing city as a total related to area and unit price respectively. The blue line is the linear fitted line and the red line is a fitted line without designating methods. From @fig-area we find that although the total price increases with area, the increase rate in each district was different with Lishui district had a notable slow rate compared with others. The increase rate indeed is just the unit price, so this is consistent with what we found from @tbl-price. We could also see that some districts had larger variance in area and total price which can simply inferred from axis scale. Pukou district had a large variance of total price with highest total price over 4000 ten-thousand yuan as well as for area.

@@

# Model

We will use two machine learning algorithms in this analysis: a multiple linear regression model, and a random forest regression model. We will randomly split our data into training and testing datasets with 80% being training data and 20% being testing data.

## Multiple Linear Regression

The multiple linear regression model is shown as:

\begin{align*}
Y = \beta_{0} + \sum^{i=1}_{n} \beta_ix_i + \epsilon = \beta_0 + \beta_1x_1 + \beta_2x_2 + \cdots + \beta_nx_n + \epsilon  
\end{align*}

@@

* $Y$ is the response variables `Total_Price`
* $x_i(i = 1,2,\cdots,n)$ are explanatory variables. In this case we have 9 explanatory variables
* $\beta_0$ is the intercept of the model
* $b_i(i = 1,2,\cdots,n)$ are regression coefficients
* $\epsilon$ is the random error

@@

model_mlg <- lm(Total_Price ~., data = train)
#summary(model_mlg)

model_rf <- randomForest(Total_Price ~., data=train, importance = TRUE)

@@

## Random Forest Regression

# Result

@@

predict_rf_test <- predict(model_rf, newdata = test)
mae_rf_test <- round(mae(test$Total_Price, predict_rf_test),1)
rmse_rf_test <- round(rmse(test$Total_Price, predict_rf_test),1)

predict_rf_train <- predict(model_rf, newdata = train)
mae_rf_train <- round(mae(train$Total_Price, predict_rf_train),1)
rmse_rf_train <- round(rmse(train$Total_Price, predict_rf_train),1)

@@

predict_mlg_test <- predict(model_mlg, newdata = test)
mae_mlg_test <- round(mae(test$Total_Price, predict_mlg_test),1)
rmse_mlg_test <- round(rmse(test$Total_Price, predict_mlg_test),1)

predict_mlg_train <- predict(model_mlg, newdata = train)
mae_mlg_train <- round(mae(train$Total_Price, predict_mlg_train),1)
rmse_mlg_train <- round(rmse(train$Total_Price, predict_mlg_train),1)

@@

MAE <- c(mae_mlg_train, mae_mlg_test, mae_rf_train, mae_rf_test)
RMSE <- c(rmse_mlg_train, rmse_mlg_test, rmse_rf_train, rmse_rf_test)
Model <- c("MLG train", "MLG test", "RF train", "RF test")
metrics <- data.frame(Model, MAE, RMSE)
kable(metrics)

@@

modelsummary(model_mlg)

ImpData <- as.data.frame(importance(model_rf))
ImpData$Var.Names <- row.names(ImpData)

ggplot(ImpData, aes(x=Var.Names, y=`%IncMSE`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`%IncMSE`), color="skyblue") +
  geom_point(aes(size = IncNodePurity), color="orange2", alpha=0.6) +
  theme_minimal() +
  labs(x = "Variable") +
  coord_flip() +
  theme(legend.position="bottom", panel.grid.major.y = element_blank(),
        panel.border = element_blank(), axis.ticks.y = element_blank())

ggplot(ImpData, aes(x=Var.Names, y=`IncNodePurity`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`IncNodePurity`), color="skyblue") +
  geom_point(aes(size = IncNodePurity), color="orange2", alpha=0.6) +
  theme_minimal() +
  labs(x = "Variable") +
  coord_flip() +
  theme(legend.position="bottom", panel.grid.major.y = element_blank(),
        panel.border = element_blank(), axis.ticks.y = element_blank())
```

>>>>

---
title: "Exploring and Predicting House Price in Nanjing: Geographically Imbalanced Distribution Across Districts and the Crucial Role of Unit Price and Bedroom Count in Predictioin"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "House prices in Nanjing have increased rapidly and became a concern in recent years. This paper examines the relationship between house price in Nanjing, structural attributes of the property, and location using open data collected from Lianjia.com. We then predict house price in Nanjing with different models. We find a geographically-imbalanced distribution of house price in Nanjing with large variance within and between each district. By comparing the MAE, RMSE, and $R^2$, we find the Random Forest model has a better prediction performance than the Multiple Linear Regression model. Unit price and number of bedrooms in the house tend to be importance features for predicting house price in Nanjing. Further work could use spatial data to include the spatial effect in the model, and tune hyperparameters to improve model performance."
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---

@@

House prices in China have grown rapidly since 2000, and prices in cities such as Shanghai, Beijing, and Shenzhen are among the highest in the world today [@citeHouseincrease]. Nanjing, which is located in the Yangtze River Delta in eastern China and approximately 300 km from Shanghai, is the capital city for Jiangsu Province, one of the most economically developed provinces in China [@citeNanjing]. House prices in Nanjing have been a concern due to increased population in recent years [@citeConcern].

In this paper, we investigate how structural attributes and the location of house affect the house price and explore the characteristics of residential housing. We are also interested in predicting house price in Nanjing using different models. We use `Python` to collect data from Lianjia.com and `R` to clean and analyze collected data. We construct a multiple linear regression model with total house price explained by nine other variables representing structural characteristics and location, and a random forest regression model with same variables. We find that the house price in Nanjing is geographically-imbalanced and even the variance within each district is large, reflecting possible income and wealth inequality. Comparing two models with Mean Absolute Error (MAE), Root Mean Squared Error (RMSE), and Coefficient of Determination ($R^2$), we find that the Random Forest model gives a better prediction performance on training data, testing data, and all datasets, indicating possible non-linear relationships between variables. We also find that unit price and bedroom count play an important role in predicting house price in Nanjing. Further work could include geospatial data to find spatial correlations and use a more comprehensive model including more factors such as surrounding environment and service amenities. We could also consider hyperparameter tuning and shrinkage methods to improvde model performance for both Multiple Linear Regression model and Random Forest model.

The remainder of this paper is structured as follows: @sec-data discusses data collection and data cleaning results, and visualizes the data by graphs and tables; @sec-model introduces two models: a Multiple Linear Regression model and a Random Forest model, and specifies parameters; @sec-result shows the coefficient estimates of the Multiple Linear Regression model, feature importance of the Random Forest model, and comparison of performance for two models; @sec-discussion discusses about model results and implications as well as weaknesses and future work.

# Data {#sec-data}

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used pakage `requests` [@citeRequests], `parsel` [@citeParsel], and `csv` [@citeCsv] in `Python` to scrape the data, and then in `R`, we used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2expand` [@citeLatex2expand] to add labels to figures, `knitr` [@citeKnitr], `broom` [@citeBroom], and `gt` [@citeGt] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to build up a Random Forest model and compare the results with Multiple Linear Regression model using different metrics. The color style of the figures was created referring to a R colors cheet-sheet [@citeRcolor].

## Data description {#sec-data_description}

The dataset in this analysis was obtained from Lianjia.com using a web scraping program in Python. Lianjia.com is the website of one of the largest estate brokerage firm in China and the source is open and accessible [@citeLianjia]. We collected 11 datasets with 30,653 observations for 11 different districts in Nanjing, China. To account for temporal variations of housing market, we specifically collected sales property price listed on 22 November, 2023 instead of posted transactions and to consider the consistency, we only collected data for residential houses and discarded data for other types of properties. The datasets includes listed sales prices and structural attributes of the properties including the floor area, the unit price per $\mbox{m}^2$, number of rooms, etc.

The original datasets were merged into one large dataset by districts with missing value removed. After obtaining 5 detailed structural characteristics by splitting `Structrual attributes` variable in original dataset, we created two new variables: `Detailed_Floor` and `Facing_South`. The variable `Detailed_Floor` was obtained from the variable `Total floor`. If the property is in a high floor, the detailed floor will be the total floor multiplied by 0.7; if the property is in a medium floor, the detailed floor will be the total floor multiplied by 0.45; and if the property is in a low floor, the detailed floor will be the total floor multiplied by 0.2. The variable `Facing_South` is a dummy variable with 1 representing the house is south-facing and 0 otherwise. Definitions and descriptions for the 10 variables are listed in @tbl-data. Most of them capture the structural attributes of the house and only `District` indicated an approximate location of the house.

@@

#### Workspace setup ####
library(tidyverse)
library(knitr)
library(here)
library(latex2exp)
library(randomForest)
library(corrplot)
library(Metrics)
library(broom)
library(gt)

@@

var <- c("Total_Price", "Unit_Price", "District", "Area", "Furnished", "Bedroom", "Living_Room", "Total_Floors", "Detailed_Floor", "Facing_South")
type <- c("Continuous", "Continuous", "Categorical", "Continuous", "Categorical", "Discrete", "Discrete", "Discrete", "Discrete", "Dummy")
def <- c("Total house price in thousand yuan", "Unit house price in thousand yuan per square meter", "District where the house is located", "Floor area of the house in square meter ", "Decoration status of the house", "Number of bedrooms", "Number of living/dining rooms", "Total floors of the building", "Floor level of the house", "Whether the house is facing south")
kable(data.frame(var, type, def), 
      col.names = c("Variable", "Type", "Definition"),
      booktabs = TRUE,
      linesep = "")
```

## Data visualization {#sec-data_visualization}

@tbl-price shows a summary for average total house price in thousand yuan, average unit price in thousand yuan/$\mbox{m}^2$, and average floor area in $\mbox{m}^2$ for 11 districts in Nanjing. We find that the highest average house price was in Jianye district while the lowest average house price was in Gaochun district, which is also consistent with the average unit price. However, the average floor area shows a different pattern. The Qinhuai district had the smallest average floor area while Jianye and Pukou districts had the largest average floor area. The difference was not very large within 30 $\mbox{m}^2$. This may relate to geographical information for each districts since the area and population differ from each district. Different from relatively centered average floor area for each districts, the average house price and unit price show a larger variance. This may relate to business activities and industrial development in each district.

@@

data |> group_by(District) |>
  summarise(avg_total = round(mean(Total_Price),1), 
            avg_unit = round(mean(Unit_Price),1),
            avg_area = round(mean(Area),1)) |>
  kable(col.names = c("District", "Average total price",
                      "Average unit price", "Average floor area"),
        booktabs = TRUE, linesep = "")
```

@fig-con, @fig-dis, and @fig-char explore the statistical features of the nine explanatory variables. @fig-con shows the distribution for variable `Area`, `Total_Price`, and `Unit_Price`, @fig-dis shows the distribution for variable `Bedroom`, `Living_Room`, `Total_Floors`, and `Detailed_Floor`. @fig-char shows the proportion of house with 4 different decoration status `Furnished` and orientations `Facing_South` in each district. We find that the total house price, the unit price, and the area were all right-skewed, which means there were some extremely high values for these variables, and the mean values were larger than the median ones. We can also find that most of the values centered in a range. The area mostly centered between 0 to 200 $\mbox{m}^2$, the total price mostly centered between 0 to 1,000,000 yuan, and the unit price had a larger range between 0 to 50,000 yuan.

@@

From @fig-dis we find that most of the listed houses had 2 or 3 bedrooms and 1 to 2 living/dining rooms. The number of rooms was relatively simple with a few houses having over 4 bedrooms and 3 living/dining rooms. However, for total floors of the building and detailed floor, they were various. We find for total floors, there are 3 bursts in approximately 5, 10, and 20, which corresponded to 3 common types of residential buildings in China. However, for detailed floor of listed house, we find that they mostly centered at lower level of the building. This may relate to the sunshine condition as the residential buildings were higher and denser recently, a lower level house may have a bad sunshine and lighting condition.

@@

We find from @fig-char that the number of houses in each districts in our data were similar excluding Gaochun district. This related to the web scraping program we used to obtain the data. However, it indicates that the total number of houses listed in Gaochun district was limited. For the orientation of the house, we find that relatively half of the house is south-facing and in Lishui and Gaochun district the proportions were even higher. It shows a tradition in China that people tend to choose houses facing south, which according to Chinese traditional Feng Shui has positive effect on someone's luck [@citeFengshui]. For decoration status of the house, the data was not that informative since type `Other` occupies a large proportion, which means the information is missing for the house. However, from existing data we find that fully furnished houses on sale has a larger proportion than partly furnished or not furnished house. This may relate to the data we collected that there were a lot of second-hand house on sale instead of newly closed. It is noticeable that houses in the Jianyi district had a much larger proportion of fully furnished house. This may related to the house type there are more fully furnished luxury apartments in Jianyi since the Central Business District (CBD) is located there.

@@

@fig-area and @fig-price show how the total house price in each district and Nanjing city as a total related to area and unit price respectively. The blue line is the linear fitted line and the red line is a fitted line without designating methods. From @fig-area we find that although the total price increases with area, the increase rate in each district was different with Lishui district had a notable slow rate compared with others. The increase rate is just the unit price, so this is consistent with @tbl-price. We could also see that some districts had larger variance in area and total price. Pukou district had a large variance of total price with highest total price over 40,000,000 yuan and largest area over 700 $\mbox{m}^2$.

@@

# Model {#sec-model}

We will use two machine learning algorithms in this analysis: a Multiple Linear Regression model (MLR), and a Random Rorest model (RF). We will randomly split our data into training and testing datasets with 80% being training data and 20% being testing data. The training data contains 24,328 observations and the testing data contains 6,082 observations. Models will be performed on training data and assessed their performances based on training data, testing data, and all datasets.

## Multiple Linear Regression {#sec-model_mlg}

The MLR model is shown as:

\begin{align*}
Y = \beta_{0} + \sum_{i=1}^{n} \beta_iX_i + \epsilon = \beta_0 + \beta_1X_1 + \beta_2X_2 + \cdots + \beta_nX_n + \epsilon  
\end{align*}

@@

* $Y$ is the response variables `Total_Price`
* $X_i(i = 1,2,\cdots,n)$ are explanatory variables. In this case we have 9 explanatory variables
* $\beta_0$ is the intercept of the model
* $\beta_i(i = 1,2,\cdots,n)$ are regression coefficients
* $\epsilon$ is the random error

The MLR model is used to estimate the coefficients ($\beta_i$) by minimizing Residual Sum of Squares (RSS), and model the linear relationship between the total house price in Nanjing `Total_Price` and multiple predictor variables `Unit_Price`, `Area`, `District`, `Furnished`, `Bedroom`, `Living_Room`, `Total_Floors`, `Detailed_Floor`, and `Facing_South`. We will use function `lm` in `R` to fit the MLR model, it will give us estimates for the coefficients as well as the standard error and t-statistics. The p-value will also be presented, which indicates whether the predictor variable has a statistically significant relationship with `Total_Price`. In general, we set the significance level $\alpha = 0.05$.

@@

model_mlg <- lm(Total_Price ~ ., data = train)
#summary(model_mlg)

model_rf <- randomForest(Total_Price ~ ., data=train, importance = TRUE)

@@

## Random Forest {#sec-model_rf}

RF is an ensemble learning method that works by growing multiple trees on training data and combining the predictions of the resulting trees [@citeRF]. It improves prediction accuracy of trees and works for both classification and regression tasks. During the process, decision trees are built on random subsets of the training data with replacement and random selection of features, and the final prediction takes the mean of individual tree prediction.

A generalized algorithm for RF with $p$ predictors can be summarized in the following steps [@citeAlgorithm]:

1. For $b=1$ to $B$:
   a. Draw a random bootstrap sample $Z^*$ of size $N$ from the training data (randomly select $N$ samples from the training set with replacement).
   b. Grow a random-forest tree $T_b$ to the bootstrapped data, at each terminal node of the tree, recursively repeat the following steps until the minimum node size $n_{min}$ is reached:
      i. Randomly select $m$ variables from the $p$ variables.
      ii. Split the node into two daughter nodes using features that provides the best split point.
2. The result is the ensemble of trees $\{T_b\}^B_1$.

The final prediction for a new data point $x$ can be expressed as

$$
{\hat{f}}^B_{\text{rf}}(x)=\frac{1}{B}\sum_{b=1}^BT_b(x)
$$
where $B$ is the number of trees, and $T_b$ is the individual regression tree.

In the process of RF, the number of trees in the forest, the number of candidate variables at each split, and the minimum size of terminal nodes are three important parameters that affect the performance of the RF model [@citeHyper]. A common choice of the number of candidate variable $m$ is $m\approx \sqrt{p}$ for classification trees, and $m=\frac{p}{3}$ for regression trees [@citeM]. We will use `randomForest` function in package `randomForest` in `R` to fit the RF model. The function by default set the minimum size of nodes $n_{min}$ to be 5, and number of trees $\text{ntree}$ to be 500. The number of candidate variables $m$ is determined by $m=\frac{p}{3}$ for regression trees as mentioned before. We will assess the importance of each predictor variable in the RF model by measuring either the percentage increase in Mean Square Error (MSE) or the increase in Node Purity for each split in trees.

# Result {#sec-result}

## Multiplie Linear Regression {#sec-result_mlg}

@tbl-model shows the summary of the multiple linear regression model. We find that `Bedroom` and `Living_Room` have negative effects on the total price, and other predictor variables have positive relationship with total price. We also notice that `District`, `Unit_Price`, and `Bedroom` have relatively strong relationship with `Total_Price`. Predictor variables are significant at level p-value $<0.05$ except for two dummy variables for `Furnished`. The dummy variables for `Not Furnished` and `Part Furnished` show large p-values, indicating they are insignificant with relation to `Total_Price`.

broom::tidy(model_mlg) |> gt() |>
  tab_spanner(label = md("Multiple Linear Regression"),
    columns = c(estimate, std.error, statistic, p.value)) |>
  fmt_number(columns = vars(estimate), decimals = 1) |>
  fmt_number(columns = vars(std.error), decimals = 1) |>
  fmt_number(columns = vars(statistic), decimals = 1) |>
  fmt_number(columns = vars(p.value), decimals = 3)
```

## Random Forest {#sec-result_mlg}

@fig-model shows the importance of variable of the random forest model based on two metrics, Mean Square Error (MSE), and Node Purity. The percentage increase in MSE ($\%\text{IncMSE}$) is calculated by how much in percentage MSE increases without the predictor. The higher value indicates more important features for making predictions. The increase in Node Purity ($\text{IncNodePurity}$) measure by how much node purity increases when splitting on a specific feature. It is usually calculated by training RSS, and same as $\%\text{IncMSE}$, the higher value indicates higher influence on prediction performance. From @fig-model we find that the three most important predictors are the same based on $\%\text{IncMSE}$ and $\text{IncNodePurity}$, which are `Unit_Price`, `Area`, and `Bedroom`. The two least important predictors are also the same, which are `Furnished` and `Facing_South`.

ImpData <- as.data.frame(importance(model_rf))
ImpData$Var.Names <- row.names(ImpData)
ImpData$Var.Names_pur <- factor(ImpData$Var.Names, levels = ImpData$Var.Names[order(ImpData$IncNodePurity)])
ImpData$Var.Names_mse <- factor(ImpData$Var.Names, levels = ImpData$Var.Names[order(ImpData$`%IncMSE`)])

ggplot(ImpData, aes(x=Var.Names_mse, y=`%IncMSE`)) +
  geom_segment( aes(x=Var.Names_mse, xend=Var.Names_mse, y=0, yend=`%IncMSE`), color="skyblue") +
  geom_point(aes(size = `%IncMSE`), color="orange2", alpha=0.6) +
  theme_minimal() +
  labs(x = "Variable") +
  coord_flip() +
  theme(legend.position="bottom", panel.grid.major.y = element_blank(),
        panel.border = element_blank(), axis.ticks.y = element_blank())

ggplot(ImpData, aes(x=Var.Names_pur, y=`IncNodePurity`)) +
  geom_segment(aes(x=Var.Names_pur, xend=Var.Names_pur, y=0, yend=`IncNodePurity`), color="skyblue") +
  geom_point(aes(size = IncNodePurity), color="orange2", alpha=0.6) +
  theme_minimal() +
  labs(x = "Variable") +
  coord_flip() +
  theme(legend.position="bottom", panel.grid.major.y = element_blank(),
        panel.border = element_blank(), axis.ticks.y = element_blank())
```

## Model Evaluation {#sec-evaluation}

| Metrics | Expression |
|:---------:|:------------:|
| MAE |$\frac{1}{n}\sum^{n}_{i=1}|y_i-\hat{y}_i|$|
| RMSE |$\sqrt{\frac{1}{n}\sum^{n}_{i=1}(y_i-\hat{y}_i)^2}$| 
| $R^2$ |$1-\frac{\sum^{n}_{i=1}(y_i-\hat{y}_i)^2}{\sum^{n}_{i=1}(y_i-\bar{y}_i)^2}$|

:Expression for MAE, RMSE, and $R^2$ {#tbl-expression}

There are three metrics being used to evaluate the two models: MAE, RMSE, and $\mbox{R}^2$. Mean Absolute Error (MAE) measures the average absolute difference between the predicted value and actual values [@citeMAE]. Root Mean Squared Error (RMSE) measures the square root of the average squared difference between the predicted value and the actual value [@citeRMSE]. The coefficient of determination ($R^2$) measures the proportion of the total variability in the response variable that can be explained by the model [@citeR2]. The expressions for the three metrics are shown in @tbl-expression. Lower values in MAE and RMSE and higher value (between 0 and 1) in $R^2$ suggest better model performance.

@@

predict_rf_all <- predict(model_rf, newdata = data)
mae_rf_all <- round(Metrics::mae(data$Total_Price, predict_rf_all),1)
rmse_rf_all <- round(Metrics::rmse(data$Total_Price, predict_rf_all),1)
r2_rf_all <- round(cor(predict_rf_all, data$Total_Price)^2,3)

predict_rf_test <- predict(model_rf, newdata = test)
mae_rf_test <- round(Metrics::mae(test$Total_Price, predict_rf_test),1)
rmse_rf_test <- round(Metrics::rmse(test$Total_Price, predict_rf_test),1)
r2_rf_test <- round(cor(predict_rf_test, test$Total_Price)^2,3)

predict_rf_train <- predict(model_rf, newdata = train)
mae_rf_train <- round(Metrics::mae(train$Total_Price, predict_rf_train),1)
rmse_rf_train <- round(Metrics::rmse(train$Total_Price, predict_rf_train),1)
r2_rf_train <- round(cor(predict_rf_train, train$Total_Price)^2,3)

@@

predict_mlg_all <- predict(model_mlg, newdata = data)
mae_mlg_all <- round(Metrics::mae(data$Total_Price, predict_mlg_all),1)
rmse_mlg_all <- round(Metrics::rmse(data$Total_Price, predict_mlg_all),1)
r2_mlg_all <- round(cor(predict_mlg_all, data$Total_Price)^2,3)

predict_mlg_test <- predict(model_mlg, newdata = test)
mae_mlg_test <- round(Metrics::mae(test$Total_Price, predict_mlg_test),1)
rmse_mlg_test <- round(Metrics::rmse(test$Total_Price, predict_mlg_test),1)
r2_mlg_test  <- round(cor(predict_mlg_test, test$Total_Price)^2,3)

predict_mlg_train <- predict(model_mlg, newdata = train)
mae_mlg_train <- round(Metrics::mae(train$Total_Price, predict_mlg_train),1)
rmse_mlg_train <- round(Metrics::rmse(train$Total_Price, predict_mlg_train),1)
r2_mlg_train <- round(cor(predict_mlg_train, train$Total_Price)^2,3)

@@

R2 <- c(r2_mlg_all, r2_mlg_train, r2_mlg_test, r2_rf_all, r2_rf_train, r2_rf_test)
MAE <- c(mae_mlg_all, mae_mlg_train, mae_mlg_test, mae_rf_all, mae_rf_train, mae_rf_test)
RMSE <- c(rmse_mlg_all, rmse_mlg_train, rmse_mlg_test, rmse_rf_all, rmse_rf_train, rmse_rf_test)
Model <- c("MLG all", "MLG train", "MLG test", "RF all", "RF train", "RF test")
metrics <- data.frame(Model, MAE, RMSE, R2)
kable(metrics, booktabs = TRUE, linesep = "", 
      col.names = c("Model", "MAE", "RMSE", "$\\mbox{R}^2$"), escape = F)

@@

@tbl-metrics shows the results for two models on both training and testing data based on three metrics. We find that overall the RF model yields a better performance on training data, testing data, and all datasets. It has a much lower MAE and RMSE compared with MLR model as well as a higher $R^2$. However, both models have a $R^2$ larger than 0.9, indicating both models could explain over 90% of the total variability in `Total_Price`. We also find that there is no large difference between training and testing performance, suggesting there is minimal overfitting for both models.

# Discussion {#sec-discussion}

## House price distribution in Nanjing {#sec-distribution}

In 2013, the Nanjing Government adjusted the boundaries and administrative divisions of Nanjing. Since then, there are 11 districts in Nanjing with Gulou, Qinhuai, Xuanwu, Jianye districts considered as inner proper while Qixia, Yuhuatai, Pukou, Jiangning, Lishui, Gaochun, Liuhe districts are considered as suburban areas of Nanjing [@citeDivision]. The difference in house price between inner city and suburban areas was also revealed in this paper. From @tbl-price we find that both the average unit price and average total price in inner proper districts are much higher than that of suburban districts. The highest average total price is in the Jianye district with value of 5,406,000 while the lowest average total price is in the Gauchun district with value of 866,800. The large difference in average total price across districts indicates disparities in economical development in each districts. The average floor area in suburban districts is slighter larger than that of inner city. It is consistent with the geographical features of the districts. Suburban area usually has larger available space for real estates, and the real estate developers have difference business strategies and target consumer for inner and suburban areas. Houses in suburban areas are usually designed as two types: one is affordable housing targeted consumers without much money for down payment, another is luxury villa targeted consumers who pursue good environment. Former type of house usually has smaller floor area and lower total price due to its location and transportation convenience. While villas are designed to have large area and better quality with good environment. As a result, we could see from @fig-price and @fig-area, both area and total price in suburban areas vary a lot within each districts especially for Pukou district. The observed variation in housing conditions not only reveals the diverse economic status but also emphasizes the potential disparities in overall quality of life within specific districts. This difference in house quality and living standards among residents within the same district reflects the broader issues of wealth and income inequality as well as social class.
